---
title: "intro-model"
author: "TODO"
format:
  html:
    self-contained: true
editor: visual
---

Goal: Fit a linear model with R.

```{r}
library(tidyverse)
```

### Data - Ames Housing

From <https://www.openintro.org/book/statdata/index.php?data=ames>

```{r}
ames <- read_csv("https://github.com/clarkfitzg/stat141/raw/refs/heads/main/data/ames2.csv")
```

```{r}
ames |> 
  ggplot(aes(x = Neighborhood, y = Sale_Price)) +
  geom_jitter() +
  theme_minimal()
```

## Q1

Which other numerical variable in `ames` has the largest correlation to `Sale_Price`?

Make a scatter plot of this variable with `Sale_Price` on the y axis.

```{r}
# TODO
```

## Q2

Are there any pairs of numerical variables in `ames` that have a negative correlation?

```{r}
# TODO
```

## Q3

Fit a linear model with using `Neighborhood` as the predictor. What are the fitted coefficients?

```{r}

```

## Q4

Calculate the means for each neighborhood. Are they the same as the predictions?

```{r}

```

## Q5

Fit a linear model using a numerical column as the predictor for `Sale_Price`. Pick the column that you think will be the best predictor. What are the fitted coefficients?

```{r}

```

## Q6

Change the above plot so that your predictor column is on the x axis, and the predicted home price is on the y axis. Why do you think they call it a linear model?

```{r}

```

## Q7

Come up with your own question and answer for the `ames` data set.

```{r}

```
