---
title: "HW 02 - Airbnb listings in Edinburgh"
format:
  html:
    self-contained: true
link-citations: true
editor: visual
---

```{r include = FALSE}
knitr::opts_chunk$set(
  out.width = "80%",
  fig.asp = 0.618,
  fig.width = 6
)
```

Once upon a time, people travelled all over the world, and some stayed in hotels and others chose to stay in other people's houses that they booked through Airbnb. Recent developments in Edinburgh regarding the growth of Airbnb and its impact on the housing market means a better understanding of the Airbnb listings is needed. Using data provided by Airbnb, we can explore how Airbnb availability and prices vary by neighbourhood.

## Warm up

Before we introduce the data, let's warm up with some simple exercises.

-   Update the YAML, changing the author name to your name, and **render** the document.

## Packages

We'll use the **tidyverse** package for much of the data wrangling and visualisation and the data lives in the **dsbox** package. These packages are already installed for you. You can load them by running the following in your Console:

```{r load-packages, message = FALSE}
library(tidyverse)


# Three options:

# 1) Read from the internet
edibnb <- read_rds("https://github.com/clarkfitzg/stat141/raw/refs/heads/main/data/edibnb.rds")

# 2) Use shared files on cloud
#edibnb = readRDS("~/shared/stat141/data/edibnb.rds")

# Alternatively, you can download on your local machine
#install.packages("devtools")
#devtools::install_github("tidyverse/dsbox")
#library(dsbox)
```

## Data

The data can be found in the **dsbox** package, and it's called edibnb. Since the dataset is distributed with the package, we don't need to load it separately; it becomes available to us when we load the package.

You can find out more about the dataset by inspecting its documentation, which you can access by running `?edibnb` in the Console or using the Help menu in RStudio to search for `edibnb`. You can also find this information [here](https://rstudio-education.github.io/dsbox/reference/edibnb.html).

# Exercises

# Q1

How many observations (rows) does the dataset have?

```{r}
# TODO
```

# Q2

What does each row in the dataset represent?

TODO- write and explain

Each column represents a variable. We can get a list of the variables in the data frame using the `names()` function.

```{r}
names(edibnb)
```

You can find descriptions of each of the variables in the help file for the dataset, which you can access by running `?edibnb` in your Console.

```{marginfigure}
**Note:** The plot will give a warning about some observations with non-finite values for price being removed. Don't worry about the warning, it simply means that 199 listings in the data didn't have prices available, so they can't be plotted.
```

## Q3

Create a faceted histogram where each facet represents a neighbourhood and displays the distribution of Airbnb prices in that neighbourhood. Think critically about whether it makes more sense to stack the facets on top of each other in a column, lay them out in a row, or wrap them around. Along with your visualisation, include your reasoning for the layout you chose for your facets.

``` r
ggplot(data = ___, mapping = aes(x = ___)) +
  geom_histogram(binwidth = ___) +
  facet_wrap(~___)
```

Copy and paste the code above below, and fill in the blanks.

```{r}

```

Let's de-construct this code:

-   `ggplot()` is the function we are using to build our plot, in layers.

-   In the first layer we always define the data frame as the first argument. Then, we define the mappings between the variables in the dataset and the **aes**thetics of the plot (e.g. x and y coordinates, colours, etc.).

-   In the next layer we represent the data with **geom**etric shapes, in this case with a histogram. You should decide what makes a reasonable bin width for the histogram by trying out a few options.

-   In the final layer we facet the data by neighbourhood.

## Q4

Deleted

## Q5

Create a visualization that will help you compare the distribution of review scores (`review_scores_rating`) across neighbourhoods. You get to decide what type of visualisation to create and there is more than one correct answer! In your answer, include a brief interpretation of how Airbnb guests rate properties in general and how the neighbourhoods compare to each other in terms of their ratings.

```{r}

```
