---
title: "intro-model"
format: html
editor: visual
---

Goal: Fit a linear model with R.

```{r}
library(tidyverse)
```

### Data - Ames Housing

From <https://www.openintro.org/book/statdata/index.php?data=ames>

```{r}
ames <- read_csv("https://github.com/clarkfitzg/stat141/raw/refs/heads/main/data/ames2.csv")
```

Let's get familiar with this data.

Make a histogram of the sale price.

```{r}

```

```{r}
ames |> 
  ggplot(aes(x = Neighborhood, y = Sale_Price)) +
  geom_jitter() +
  theme_minimal()
```

## Q1

Which numerical variable in `ames` has the largest correlation to `Sale_Price`?

Make a scatter plot of this variable with `Sale_Price` on the y axis.

```{r}
# TODO
```

## Q2

Are there any pairs of numerical variables that have a negative correlation?

```{r}
# TODO
```

## Q3

Fit a linear model with using `Neighborhood` as the predictor. What are the predictions in each neighborhood?

```{r}

```

## Q4

Calculate the means for each neighborhood. Are they the same as the predictions?

```{r}

```
