---
title: "PRACTICE midterm"
author: "TODO"
format:
  html:
    self-contained: true
editor: visual
---

```{r, warning=FALSE, message=FALSE}
library(tidyverse)
```

### Q1

What does one row in the `msleep` data represent?

### Q2

How many rows and columns are in the `msleep` data?

```{r}

```

### Q3

Which animal sleeps the most? The least?

```{r}

```

### Q4

Which animal sleeps more, cats or dogs?

```{r}

```

### Q5

Create a data frame containing the median values of `sleep_total` for each of the values of `vore`, namely, carnivore, omnivore, and herbivore.

```{r}

```

### Q6

Create a scatter plot with `sleep_total` on the x axis and `sleep_rem` on the y axis.

```{r}

```

### Q7

Comment on the above plot. What does it show?

### Q8

Create a new column `prop_brain` representing the proportion of brain weight relative to body weight. That is `brainwt / bodywt`. Create a scatter plot with `prop_brain` on the x axis, and `sleep_total` on the y axis.

```{r}

```

### Q9

Comment on the above plot. What does it show?

### Q10

Create a histogram of `total_sleep`

```{r}

```

### Q11

Comment on the above plot. What does it show?

### Q12

```{r}
mutate(msleep, domesticated = (conservation == "domesticated")) |>
  ggplot(aes(x = domesticated, y = sleep_total)) +
  geom_boxplot() +
  labs(y = "total sleep (hours)") +
  theme_minimal()
```

Comment on the above plot. What does it show?

### Q13

Come up with an interesting question that you might be able to answer using the `msleep` data.

### Q14

Create an original and different plot of the `msleep` data. You may choose to answer the above question you asked, or not.

### Q15

Comment on what your plot shows.
