---
title: "Project key insight"
author: "TODO"
format:
  html:
    self-contained: true
editor: visual
---

```{r}
library(tidyverse)
```

## 1 data

*Load your data, show the first few rows, and describe what each row represents. Write a paragraph explaining the data to a fellow student in Stat 141.*

```{r}

```

TODO: Write answer here.

## 2 key insight

Make a presentation quality graph highlighting your key insight that includes the following:

1.  Title
2.  Clear labels for x and y axes
3.  Good choices of aesthetics
4.  Good, efficient use of visual space
5.  Text annotations for notable data points
6.  Legend if necessary

```{r}
# TODO
```

## 3 discussion

*Describe your key insight in 1-3 paragraphs. Why is it interesting? Did the data surprise you? Who would find this insight valuable? How might people apply or act on this insight?*

TODO: Write answer here.

## 4 future steps

*Describe in 1 paragraph a new question or direction that you would like to pursue if you had more time, more statistical knowledge, or different data.*

TODO: Write answer here.
