---
title: "Project linear model"
author: "TODO"
format:
  html:
    self-contained: true
editor: visual
---

For this stage of the project we'll fit a linear model.

```{r}
library(tidyverse)
```

## 1 Variables

*Load the data and find a numerical column that you can use as a response (y value) and another column that you can use as a predictor (x value). Show 6 rows of the data with these two columns.*

```{r}

```

*Describe why this prediction problem is interesting to you or someone else. Who would care about these predicted values, and why?*

TODO- write answer.

## 2 Scatter plot

*Make a scatter plot with the response value on the y axis and the predictor value on the x axis. Use `geom_smooth(method = "lm")` to add the least squares line. Does a linear model seem appropriate?*

```{r}
# TODO
```

## 3 Model

*Fit a linear model, save it in the variable `mod1` and print it.*

```{r}
# mod1 <- lm( TODO
# print(mod1)
```

*Write the mathematical model it represents, using the fitted coefficients to replace the ? symbols in the equation.*

$$
Y_i = ? + ?X_i + e_i
$$\

## 4 Predict
