---
title: "Simpson's"
format: html
editor: visual
---

Goal: Explain Simpson's paradox.

```{r}
library(tidyverse)

ucbadmit <- read_csv("https://github.com/clarkfitzg/stat141/raw/refs/heads/main/data/ucbadmit.csv")
```

## 1- UCB admissions

`ucbadmit` contains data on applicants to graduate school at Berkeley for the six largest departments in 1973 classified by admission and sex.

```{r}
ucbadmit %>%
  count(gender, admit)
```

1.  What proportion of males were admitted?
2.  What proportion of females were admitted?
3.  Does admission appear to be fair with regards to gender?

## 2 - Department A

```{r}
ucbadmit %>%
  count(dept, gender, admit)
```

1.  What proportion of males were admitted in department A?
2.  What proportion of females were admitted in department A?
3.  Does admission appear to be fair with regards to gender in department A?

## 3 - Extending to all departments

```{r}
ggplot(ucbadmit, aes(y = gender, fill = admit)) +
  geom_bar(position = "fill") +
  facet_wrap(. ~ dept) +
  scale_x_continuous(labels = scales::label_percent()) +
  labs(title = "Admissions by gender and department",
       x = NULL, y = NULL, fill = NULL) +
  theme(legend.position = "bottom")
```

1.  Is this the right choice of color for the plot? If not, how should we change it?
2.  Does admission appear to be fair with regards to gender?

4.625

```{r}
ucbadmit |> 
  group_by(dept) |>
  summarize(admitted = 100*sum(admit == "Admitted") / n()) |>
  ggplot(aes(x = gender, y = dept)) +
  
```
